%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Zhenguo Chen} % Your name
\address{1320 Wisteria, APT 4613, Ann Arbor, MI 48104} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{Phone: 3033597579 \ email:  \href{mailto:Zhenguo.Chen@colorado.edu}{Zhenguo.Chen@colorado.edu}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Colorado Boulder, Colorado, USA} \hfill {\em Aug 2016 - May 2018} 
\\ College of Engineering and Applied Science
\\ Master's Degree: Computer Science \hfill { GPA: 4.0 } 
\smallskip
\\{\bf Nankai University, Tianjin, China} \hfill {\em Aug 2012 - May 2016} 
\\ B.S. in Information Security
\\ B.A. in Law \hfill { Overall GPA: 3.5 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Interests \ & Machine Learning, Computer Vision, Natural Language Processing \\
Skills \ & Python, C++, TensorFlow, Pytorch, Django, Docker \\
\end{tabular}

\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL Experience}

\begin{rSubsection}{Clinc, Inc.}{June 2018 - Present}{Software Engineer (Core AI R$\&$D Team)}{Ann Arbor}
\item Maintained and improved Clinc NLU with various deep neural network models, such as attention-BiLSTM, Transformer, Encoder-Decoder.
\item Researched and Enhanced Clinc NLU capabilities, including classification, named-entity recognition, entity-linking, and out-of-domain detection.
\item Built and integrated models with business logic server for multiple clients, including top 10 banks in US, Europe with millions of users.
\item Devised, developed and delivered solutions for challenging customer problems.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Out-of-Domain Detection}{Jan 2020 - Present }{Clinc Research Project}{}
\item Implemented Prototypical Network to support OOD detection for datasets both with and without OOD training data.
\item Evaluated multiple models (Proto/Bert/Fasttext/SVM) across multiple datasets.
\item Researched, optimized OOD detection models as potential solutions to improve Clinc NLU capability.
\end{rSubsection}

\begin{rSubsection}{Enhance Dialog System with Slot Relation Extraction}{Nov 2019 - Present }{Clinc Research Project}{}
\item Built state-of-the-art slot relation extraction (RE) models (attention $\&$ transformer).
\item Designed and conducted experiments to evaluate RE models and built an end-to-end solution.
\item Integrated slot relation extractors with Clinc dialog system to support customer projects.
\item Paper submitted to ACL2020.
\end{rSubsection}

\begin{rSubsection}{Slot Tree for Handling Recursive Queries}{Sept 2018 - Jan 2019 }{Clinc Production Project}{}
\item Devised and developed algorithms to generate trees structure (Slot Tree) for named-entities.
\item Applied slot tree to handle recursive queries, which was used in production. 
\item Designed user-friendly response generation for recursive queries.
\end{rSubsection}

\begin{rSubsection}{Image Captioning Using Neural Network}{Jan - May 2017 }{Master's Project, CU Boulder}{Advisor: Chris Ketelsen}
\item Built Convolution Neural Network (VGG16/19) and NLU model (LSTM) to extract features and generate descriptive captions for images.
\item Designed and developed web pages as an end-to-end solution for user.
\item YouTube video available \href{https://www.youtube.com/watch?v=f2waevH1b6I}{here}
\end{rSubsection}

\begin{rSubsection}{Autonomous Vehicle with Obstacle Detection}{Jan - May 2017 }{Master's Project, CU Boulder}{Advisor: Chris Heckman}
\item Built SLAM (Simultaneous localization and mapping) on robot for localization.
\item Built real-time object detection module with OpenCV.
\item Integrated modules in ROS (Robot OS) to facilitate communication between components.
\end{rSubsection}

\begin{rSubsection}{NXP Asymmetric Encryption Implementation and Optimization}{Jan - Jun 2016 }{Undergrad Dissertation, Nankai University}{Advisor: Zheli Liu}
\item Built RSA (cryptosystem) and optimized it with Montgomery algorithm.
\item Programmed and utilized NXP Fame2 co-processor to accelerate RSA encryption.
\item Built ECC (cryptosystem) and optimized it with Jacobian coordinate.
\item Programmed and utilized NXP Fame2 co-processor to accelerate ECC encryption.
\end{rSubsection}

\begin{rSubsection}{Dual Deception Secret Sharing Improvement}{Jan - Jun 2016 }{Undergrad Project, Nankai University}{Advisor: Zhaohui Li}
\item Implemented Random Grid-based Visual Secret Sharing algorithm for secret sharing.
\item Improved RGVSS with dual deception (hiding secret information in multiple images).
\item Built dual deception RGVSS and evaluated its security.
\end{rSubsection}

\begin{rSubsection}{Book Recommendation System Based on Douban Reviews}{Mar 2014 - Apr 2015}{Undergrad Project, Nankai University}{Advisor: Jie Liu}
\item Collected and parsed user data from Douban (a book review website).
\item Applied Lucene as recommendation engine to model users' interest.
\item Designed and developed backend for final website.
\end{rSubsection}

\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Teaching}

\begin{rSubsection}{}{}{}{}
\item \normalfont Teaching Assistant CSCI3155 Principle of Programming Language, CU Boulder
\item \normalfont Graduate Course Assistant CSCI5622 Machine Leanring, CU Boulder
\end{rSubsection}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Academic Achievements} 
%  Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
% \item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
% \end{rSection}

% \newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Cirrucular} \itemsep -3pt
% \item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
% \item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
% \item Winner of Inter Departmental Football Competition 2015.
% \item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
% \item Worked for a start-up company Named OUST as a Regional Marketing Manager
% %\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
%  %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
%  %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
%  %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

% \end{rSection}

\begin{rSection}{Personal Traits}

\begin{rSubsection}{}{}{}{}
\item Highly motivated and eager to learn new things.
\item Ability to work as an individual as well as in group.
\end{rSubsection}

\end{rSection}
\end{document}
